A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-07-29 vignette/Manuscript2Word.Rmd
Spelling
Add custom styles to template

---
title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
author:
  - Paul Melloy:
      email: Paul.Melloy@usq.edu.au
      institute: USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Adam H. Sparks:
      institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
      reference_docx: "Manuscript2Word_Template.docx"
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
abstract: |
         Insert abstract here.
---
<!-- Should we use the word "fungicide" in the title so it is more searchable for fungicide management? -->

@@

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
source(here("R/reportP.R"))
```

@@

## Core ideas
<!-- up to 85 words per idea -->

## Authors - affiliations and email address

@@

## Abrebiations

>>>>

---
title: "A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean"
author:
  - Paul Melloy:
      email: Paul.Melloy@usq.edu.au
      institute: USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Adam H. Sparks:
      institute: USQ
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
  - UFV: Universidade Federal de Viçosa, Departamento de Fitopatologia, 36570-000 MG, Brazil
date: "Last Edit: `r format(Sys.time(), '%d %B, %Y')`"
output:
   word_document:
      reference_docx: "Manuscript2Word_Template.docx"
      md_extensions: +styles
      pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: "../Mungbean.bib"
biblio-style: apalike
link-citations: yes
abstract: |
         **Abstract:** Insert abstract here.
---

@@

# Data
PM_Mdat <- read.csv(here("cache/PM_MB_updated.csv"))
load(file = here("cache/Meta-analysisData.Rdata"))
load(file = here("cache/PreliminaryData.Rdata"))
source(here("R/reportP.R"))
```
::: {custom-style="Art_type"}
Type of Paper: Article
:::

::: {custom-style="keywords"}
**Keywords:** meta-analysis, powdery mildew, mungbean, fungicide                                                      
:::
<!-- Is anyone aware of a way to put the "Type of paper" text above the renderd YAML header? ... or ... Specify extra text in the header which is rendered as a different style? 
I am considering dropping the lua files and just codeing in the different styles to suit the MDPI_Agronomy_Template.docx -->

@@

@@

## Abbreviations
